Restructuring Data for Exascale Scientific Productivity

### 2016-04-09 papers/2016-Supercomputing/paper.tex
blinded for review

\numberofauthors{1}
\author{
  \alignauthor {
    Hasan Abbasi\footnotemark[3]~~,
    Jay Lofstead\footnotemark[1]~~,
    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
    Jong Choi\footnotemark[3]~~,
    Matthew Curry\footnotemark[1]~~,\\
    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
    Tahsin Kurc\footnotemark[9]~~,
    Qing Liu\footnotemark[3]~~,
    Jeremy Logan\footnotemark[4]~~,
    Carlos Maltzahn\footnotemark[2]~~,
    Manish Parashar\footnotemark[5]~~,\\
    Norbert Podhorzski\footnotemark[3]~~,
    Feiyi Wang\footnotemark[3]~~,
    Matthew Wolf\footnotemark[7]~~,
    Ben Whitney\footnotemark[6]~~,
    C. S. Chang\footnotemark[8]~~,
    Michael Churchill\footnotemark[8]~~,
    Stephane Ethier\footnotemark[8]~~
  }\\
  \footnotemark[1]~~Sandia National Laboratories,
  \footnotemark[2]~~University of California Santa Cruz,\\
  \footnotemark[3]~~Oak Ridge National Laboratory,
  \footnotemark[4]~~U. Tenn. Knoxville,
  \footnotemark[5]~~Rutgers University,\\
  \footnotemark[6]~~Brown University,
  \footnotemark[7]~~Georgia Tech,
  \footnotemark[8]~~PPPL,
  \footnotemark[9]~~Stony Brook
}
\maketitle

@@

Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.

>>>>

\numberofauthors{1}
\author{blinded for review}
%\author{
%  \alignauthor {
%    Hasan Abbasi\footnotemark[3]~~,
%    Jay Lofstead\footnotemark[1]~~,
%    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
%    Jong Choi\footnotemark[3]~~,
%    Matthew Curry\footnotemark[1]~~,\\
%    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
%    Tahsin Kurc\footnotemark[9]~~,
%    Qing Liu\footnotemark[3]~~,
%    Jeremy Logan\footnotemark[4]~~,
%    Carlos Maltzahn\footnotemark[2]~~,
%    Manish Parashar\footnotemark[5]~~,\\
%    Norbert Podhorzski\footnotemark[3]~~,
%    Feiyi Wang\footnotemark[3]~~,
%    Matthew Wolf\footnotemark[7]~~,
%    Ben Whitney\footnotemark[6]~~,
%    C. S. Chang\footnotemark[8]~~,
%    Michael Churchill\footnotemark[8]~~,
%    Stephane Ethier\footnotemark[8]~~
%  }\\
%  \footnotemark[1]~~Sandia National Laboratories,
%  \footnotemark[2]~~University of California Santa Cruz,\\
%  \footnotemark[3]~~Oak Ridge National Laboratory,
%  \footnotemark[4]~~U. Tenn. Knoxville,
%  \footnotemark[5]~~Rutgers University,\\
%  \footnotemark[6]~~Brown University,
%  \footnotemark[7]~~Georgia Tech,
%  \footnotemark[8]~~PPPL,
%  \footnotemark[9]~~Stony Brook
%}
\maketitle

@@

blinded for review

%Sandia National Laboratories is a multi-program laboratory managed and operated
%by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
%Corporation, for the U.S. Department of Energy's National Nuclear Security
%Administration under contract DE-AC04-94AL85000.
